Efficient implementation of kernel filtering

### 2007-06-29 article/Article.tex
corrected equation refs and added ref to darcs repo
darcs-hash:20070629055044-fafb9-0559a71a743b7425fd70c7929e013a1f9bd5ec64.gz

Using the same strategy, the standard deviation can be efficiently
computed.  It requires an accumulator image of the squared pixels
values, which can be efficiently computed at the same time as the
original accumulator image. The update formulas are provided in
Equations \ref{eq:accum}, \ref{eq:accSum},
\ref{eq:accum2}, \ref{eq:accSum2} and \ref{eq:accumSigma}.

@@

\section{ITK implementation}
The filters discusses in this article are contained in 3 packages --
{\em consolidatedMorphology}, {\em fastRankMean} and {\em
boxConvolution}. The most recent versions of these packages can be
obtained from {\bf link to Gaetan's darcs repo}. All of the packages
include multithreaded filters and include many examples. Unless
indicated otherwise, all filters will behave basically the same way as
other kernel filters, requiring either a radius or a neighborhood to
be specified.

>>>>

Using the same strategy, the standard deviation can be efficiently
computed.  It requires an accumulator image of the squared pixels
values, which can be efficiently computed at the same time as the
original accumulator image. The update formulas are provided in
Equations \ref{eq:accum2}, \ref{eq:accSum2} and \ref{eq:accumSigma}.

@@

\section{ITK implementation}
The filters discusses in this article are contained in 3 packages --
{\em consolidatedMorphology}, {\em fastRankMean} and {\em
boxConvolution}. The most recent versions of these packages can be
obtained from {\bf http://voxel.jouy.inra.fr/darcsweb/}. All of the packages
include multithreaded filters and include many examples. Unless
indicated otherwise, all filters will behave basically the same way as
other kernel filters, requiring either a radius or a neighborhood to
be specified.
